\Title

### 2021-05-11 latex/paper/main.tex
Updated the experimental results section. Everything is done its first draft except the conclusion and the proof of theorem 10.

The results of Theorem \ref{thm:acrobot-energy-stabilization} lead naturally to
the idea of energy regulation: one could employ a supervisor which switches
between injection and dissipation constraints to stabilize a desired energy
level \(\bar{E}\).
For instance, the supervisor could inject energy when \(E(q_u,p_u) < \bar{E}\) 
and dissipate energy when \(E(q_u,p_u) > \bar{E}\), with some hysteresis to
avoid infinite switching.
As we shall see, such a simple supervisor will not produce human-like
oscillations or rotations.
However, it will allow the acrobot to stabilize some peak angle of oscillation
\(\bar{q}_u \in \, ]0,\pi[\) so that \(E(\pm \bar{q}_u,0) = \bar{E}\),
or some peak rotational momentum
\(\bar{p}_u \in \, ]\sqrt{60m^2gl^3}, \bar{\rho}[\) where
\(E(0,\pm \bar{p}_u) = \bar{E}\).

@@

\textbf{TODO: rework this section. In simulation we showed that we gain energy
everywhere. Here we only gain energy up to speed 0.195 because of friction.}
We performed the following tests.

\begin{enumerate}
    \item \textbf{Baseline Test:} 
    we initialized the acrobot at 
    \((q_u,p_u) \approx \left(\frac{\pi}{8},0\right)\). 
    The resulting orbit is shown in Figure \ref{fig:acrobot-unperturbed-orbit};
    the acrobot is clearly gaining energy over time.

\begin{figure}
    \centering
    \begin{subfigure}[t]{0.49\linewidth}
        \includegraphics[width=\linewidth]{acrobot_unperturbed_orbit.png}
        \caption{The baseline test.}
        \label{fig:acrobot-unperturbed-orbit}
    \end{subfigure}
    \begin{subfigure}[t]{0.49\linewidth}
        \includegraphics[width=\linewidth]{acrobot_stopped_orbit.png}
        \caption{Acrobot orbit before (blue) and after (red) stopping.}
        \label{fig:acrobot-stopped-orbit}
    \end{subfigure}
    \caption{The physical acrobot's orbit during baseline and stop tests.}
\end{figure}

\item \textbf{Stop Test:}
    we initialized the acrobot at 
    \((q_u,p_u) \approx \left(\pi,0\right)\), let it run for 15
    seconds, then stopped it at the bottom of its arc.
    The resulting orbit is shown in Figure \ref{fig:acrobot-stopped-orbit}.
    The blue curves correspond to the orbit before the disturbance, while the red
    spiral confirms that the acrobot begins oscillating after it is stopped.
    Despite the disturbance, it gains energy and eventually starts rotating
    again.

\item \textbf{Push Test:}
    to see how the acrobot responds when pushed, we allowed
    the acrobot to rotate undisturbed for 15 seconds and then pushed it in its
    direction of motion.
    The orbit in Figure \ref{fig:acrobot-fpush-orbit} shows that the acrobot speeds
    up to rotate with energy \(E(0,-0.22)\), but then slows down until it reaches a
    rotation with energy \(E(0,-0.195)\).
    We repeated this test by pushing the acrobot against its direction of motion.
    The orbit in Figure \ref{fig:acrobot-rpush-orbit} demonstrates that the acrobot
    responds by readily changing direction, and quickly achieves its maximum speed
    with energy \(E(0,0.195)\).

    These push tests suggest that our VNHC injects energy into Wang's acrobot on
    \(\mathcal{O}_2(0.195)\).
\end{enumerate}

@@

\subsection{Summary of Results} 
These experiments demonstrate that VNHCs are excellent tools for injecting
energy.
In particular, energy injection through VNHCs appears to be robust against a
variety of disturbances, including significant model mismatch, friction, and
sensor noise.

>>>>

The results of Theorem \ref{thm:acrobot-energy-stabilization} lead naturally to
the idea of energy regulation: one could employ a supervisor which switches
between injection and dissipation constraints to stabilize a desired energy
level \(\bar{E}\).
For instance, the supervisor could inject energy when \(E(q_u,p_u) < \bar{E}\) 
and dissipate energy when \(E(q_u,p_u) > \bar{E}\), with some hysteresis to
avoid infinite switching.

@@

In Section \ref{sec:simulations} we showed that VNHCs can be used for energy
injection, dissipation, and regulation. 
We will now demonstrate that VNHC-based giant motion is robust to external
disturbances by implementing our VNHC on the SUGAR system.
We performed the following tests.

\begin{enumerate}
    \item \textbf{Baseline Test:} 
    we initialized the acrobot at 
    \((q_u,p_u) \approx \left(\pi/8,0\right)\). 
    The resulting orbit in Figure \ref{fig:acrobot-unperturbed-orbit} shows
    the acrobot clearly gaining energy over time.
    Its motion looks similar to that of the energy injection simulation (Figure
    \ref{fig:acrobot-in-orbit}), though the acrobot appears to stop gaining
    energy once it reaches a rotation with energy \(E(0,0.195)\).

\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{acrobot_unperturbed_orbit.png}
    \caption{The physical acrobot's orbit during the baseline energy injection test.}
    \label{fig:acrobot-unperturbed-orbit}
\end{figure}

\item \textbf{Stop Test:}
    we initialized the acrobot at 
    \((q_u,p_u) \approx \left(\pi,0\right)\), let it run for 15
    seconds, then stopped it at the bottom of its arc.
    The resulting orbit is shown in Figure \ref{fig:acrobot-stopped-orbit}.
    The blue rotation curve corresponds to the orbit before the disturbance,
    while the red spiral confirms that the acrobot begins oscillating after it
    is stopped.  
    Despite the disturbance, it gains energy and eventually starts rotating
    again.

\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{acrobot_stopped_orbit.png}
    \caption{The physical acrobot's orbit before (blue) and after (red) stopping.}
    \label{fig:acrobot-stopped-orbit}
\end{figure}

\item \textbf{Push Test:}
    to see how the acrobot responds when pushed, we allowed
    the acrobot to rotate undisturbed for 15 seconds and then pushed it in its
    direction of motion.
    The orbit in Figure \ref{fig:acrobot-fpush-orbit} shows that the acrobot,
    when pushed, rotates with energy \(E(0,-0.22)\), but then slows down until
    it reaches a rotation with energy \(E(0,-0.195)\).
    We repeated this test by pushing the acrobot against its direction of motion.
    The orbit in Figure \ref{fig:acrobot-rpush-orbit} demonstrates that the acrobot
    readily changes direction, and quickly achieves its maximum speed
    with energy \(E(0,0.195)\).
\end{enumerate}

In simulation, the acrobot was able to gain energy even when initialized
with energy \(E(q_u,p_u) > E(0,0.195)\). 
The baseline and push tests suggest that our VNHC injects energy into the SUGAR
system only on \(\mathcal{O}_2(0.195)\).
This difference between simulation and implementation is likely due to
friction.

@@

We had hoped to show experimental results for dissipation and
oscillation/rotation regulation, but unfortunately our Dynamixel RX24F servo
motor broke before we could perform these experiments.
These motors are no longer in production at the time of writing, so the SUGAR
system has been retired for the time being.

\subsection{Summary of Results} 
We performed three tests on the SUGAR system: a baseline energy injection test,
a stop test, and a push test.
These experiments demonstrate that VNHC-based energy injection is robust to
significant model mismatch, friction, sensor noise, discretized control
implementation, rate-limited measurement and control signals, and dramatic
external disturbances.
